Approximation as Differentiation

### 2025-05-08 main/formal-structures.tex
Done for now.

@@

Now consider the total category $\Fam(\LatGal)$, which is our basic setting for interpreting first-order
programs. This has as objects $(X, \partial X)$, all pairs of a set $X$ and and for every $x \in X$, a bounded
lattice $\partial X_x$, and as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs $(f, \partial f)$ of
a function $f: X \to Y$ and for every $x \in X$, a Galois connection $\partial f(x): \partial X(x) \to
\partial Y(f(x))$, as required. The role of the pullback (reindexing) along $f$ in the composition $(g,
\partial g) \comp (f, \partial f) = (g \comp f, \reindex{\partial g}{f} \comp \partial f)$ is to select the
appropriate lattice of approximations and Galois connection at each point, using the baseline (unapproximated)
function $f$.

>>>>

\begin{definition}[Category of families]
For any category $\cat{C}$ define $\Fam(\cat{C})$ to be the Grothendieck construction
$\Grothendieck{X}\Func{X}{\cat{C}}$.
\end{definition}

\noindent In $\Fam(\cat{C})$ the objects $(X, \partial X)$ are thus sets $X$ paired with indexed families
$\partial X$ in $\Fam(X,\cat{C})$ and morphisms $(f, \partial f): (X, \partial X) \to (Y, \partial Y)$ are
functions $f: X \to Y$ paired with morphisms $\partial f: \partial X \to \reindex{\partial Y}{f}$ in
$\Fam(X,\cat{C})$.

@@

Now consider the total category $\Fam(\LatGal)$, which is our basic setting for interpreting first-order
programs for Galois slicing. This has as objects $(X, \partial X)$, all pairs of a set $X$ and and for every
$x \in X$, a bounded lattice $\partial X_x$, and as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs
$(f, \partial f)$ of a function $f: X \to Y$ and for every $x \in X$, a Galois connection $\partial f(x):
\partial X(x) \to \partial Y(f(x))$, as required. The pullback (reindexing) along $f$ in the composition $(g,
\partial g) \comp (f, \partial f) = (g \comp f, \reindex{\partial g}{f} \comp \partial f)$ selects the
appropriate lattice of approximations and Galois connection at each point, using the baseline (unapproximated)
function $f$.
